Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-04 manuscript.Rmd
Working on forecast models.

```{r plotSmallMultiples}

@@

# Plotting function    
ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))

@@

```{r plotScatter}

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(title)

H <- unique.titles$Hodge

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))
final.list.index <- full_join(final.list, hIndex, by = "title")

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
#    theme_bw() 
final.list.index$scaleScore <- scale(final.list.index$n)
final.list.index$hScaled <- scale(final.list.index$h5Index)
final.list.index <- arrange(final.list.index, scaleScore)

x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
    xlim(c(-3, 3))

>>>>

```{r plotSmallMultiples}
# Remove 2014 & 2015

@@

# Plotting function    
ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))

@@

```{r articleSummary}
#---------------------------------
# Create new data file 
#---------------------------------
articles.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title) %>%
    rename(Year = year, Journal= title)

scopus.df <- read.csv("scopus.csv")
articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))

#---------------------------------
# Create new variables
#---------------------------------

articles.df<- articles.df %>% 
    mutate(notCited = N - N * (X..Not.Cited/100))

articles.df<- articles.df %>% group_by(Year) %>%
    summarize(HD.N = sum(N, na.rm=TRUE), 
              Scopus.N = sum(Documents, na.rm=TRUE),
              Uncited.N = sum(notCited, na.rm=TRUE)) %>%
    mutate(HD.N = ifelse(HD.N == 0, NA, HD.N), Scopus.N = ifelse(Scopus.N == 0, NA, Scopus.N))

articles.df$Scopus.N[articles.df$Year > 2011] <- NA
articles.df$Uncited.N[articles.df$Year > 2011] <- NA
articles.df$Uncited.N <- ifelse(articles.df$Uncited.N == 0, NA, articles.df$Uncited.N)

articles.df.melted <- articles.df %>% 
    reshape2::melt(id.vars = "Year")

#--------------------------------------------
#Create time series data to estimate uncited
#--------------------------------------------

uncited.ts <- as.vector(na.omit(articles.df$Uncited.N))
uncited.ts <- ts(uncited.ts, frequency = 16, start = c(1996,1))

foreward <- auto.arima(uncited.ts)
uncited.forecast <-data.frame(forecast(fit, 2))
forecast.estimated <- uncited.forecast$Point.Forecast
forecast.years <- c(2012, 2013)

backcast <- rev(uncited.ts)
backcast <- auto.arima(backcast)
uncited.backcast <- data.frame(forecast(backcast, 7))
backcast.estimated <- rev(uncited.backcast$Point.Forecast)
backcast.years <- c(1989:1995)

Year <- c(backcast.years, forecast.years)
value <- c(backcast.estimated, forecast.estimated)
uncited.df <- data.frame(cbind(Year, value))
uncited.df$variable <- "Estimated"

#articles.df.melted <- rbind(articles.df.melted, uncited.df)

ggplot(na.omit(articles.df.melted),  aes(Year, value, colour = variable)) + 
    geom_line() + 
    geom_point() + 
    scale_color_manual(values=cp) + 
    geom_point(data = uncited.df, aes(Year, value, colour = variable)) + 
    ylim(c(0, 2700))
